Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2013-03-24 documents/mixtures/mixture_models.tex

The general equation for $\alpha^{\ser(n)}$ is (\citealt{ciotti} equation~5):
\begin{eqnarray}
\gamma(2 n, \alpha^{\ser(n)}) &=& \frac{\Gamma(2 n)}{2}
\\
\gamma(q, x) &\equiv& \int_0^x \exp(-t) \, t^{q-1} \, \mathrm{d}t
\quad ,
\end{eqnarray}
where $\gamma(\cdot)$ is the \emph{left} or \emph{lower} incomplete
gamma function.  Fortunately for us, this can be evaluated using
\begin{eqnarray}
\alpha^{\ser(n)} &=& \texttt{gammaincinv}(2 n, \, \frac{1}{2})
\end{eqnarray}
using the \texttt{gammaincinv} (inverse incomplete gamma) function in the
\project{scipy.special} library.

>>>>

The general equation for $\alpha^{\ser(n)}$ is (\citealt{ciotti} equation~5):
\begin{eqnarray}
\gamma(2 n, \alpha^{\ser(n)}) &=& \frac{\Gamma(2 n)}{2}
\\
\gamma(q, x) &\equiv& \int_0^x \exp(-t) \, t^{q-1} \, \mathrm{d}t
\quad ,
\end{eqnarray}
where $\gamma(\cdot)$ is the lower incomplete gamma function.
Fortunately for us, this can be evaluated using
\begin{eqnarray}
\alpha^{\ser(n)} &=& \texttt{gammaincinv}(2 n, \, \frac{1}{2})
\end{eqnarray}
where \texttt{gammaincinv} is the inverse incomplete gamma function implemented
in the \project{scipy.special} library.\footnote{\url{http://scipy.org}}
